---
title: "Expulsion"
author: "Merly Klaas"
date: "10/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rio)
library(ggplot2)
library(readr)
library(here)
library(janitor)
library(skimr)
library(dplyr)
```

Importing the data set

```{r}
expl <- read.csv(here("data", "Expulsions.csv")) %>% 
  clean_names() %>%  
  as_tibble()
```

Dataset with no negative values across all variables. 

```{r}
expl1 <- expl
expl1[expl1 < 0] <- NA

expl1 <- expl1 %>% 
  drop_na()
expl1

```

## Explusion of preschool children, by race/ethnicity and gender, disability status


```{r}
preschool_expl <- expl %>% 
  select(1:24)
preschool_expl[preschool_expl < 0] <- NA

preschool_expl <- preschool_expl %>% 
  drop_na()
preschool_expl
```

## Expulsion of students with educational services, by race/ethnicity, gender, disability status

```{r}
w_edu_expl <- expl %>% 
  select (1:8, 29:48, 85:103)
w_edu_expl[w_edu_expl <0] <- NA

w_edu_expl <- w_edu_expl %>% 
  drop_na()
colnames(w_edu_expl)
```

## Expulsion of students without educational services, by race/etchnicity, gender, disability status

```{r}
wo_edu_expl <- expl %>% 
  select (1:8, 49:64, 104:122)
wo_edu_expl[wo_edu_expl <0] <- NA
wo_edu_expl <- wo_edu_expl %>% 
  drop_na()
colnames(wo_edu_expl)
```

## Expulsion of students under zero tolerance policy

```{r}
zero_pol_expl <- expl %>% 
  select(1:8, 65:84, 123:142)
zero_pol_expl[zero_pol_expl <0] <- NA
zero_pol_expl <- zero_pol_expl %>% 
  drop_na()
colnames(zero_pol_expl)

```
