---
title: "Suspension"
author: "Merly Klaas"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rio)
library(ggplot2)
library(readr)
library(here)
library(janitor)
library(skimr)
library(dplyr)
```

## Importing dataset

```{r}
susp <- read.csv(here("data", "Suspensions.csv")) %>% 
  clean_names() %>%  
  as_tibble()

```

Dataset with no negative values across all variables. 

```{r}
susp1 <- susp
susp1[susp1 < 0] <- NA

susp1 <- susp1 %>% 
  drop_na()
```

## Preschool students suspension by race/ethnicity, gender, disability status
* Only one out-of-school suspension
```{r}
preschool_susp <- susp %>% 
  select (1:8, 10:28, 49:50 )
preschool_susp[preschool_susp < 0] <- NA

preschool_susp <- preschool_susp %>% 
  drop_na()
preschool_susp
```
* more than one out-of-school suspensions
```{r}
preschool_more_susp <- 
  preschool_more_susp <- susp %>% 
  select (1:8, 29:50 )
preschool_more_susp[preschool_more_susp < 0] <- NA

preschool_more_susp <- preschool_more_susp %>% 
  drop_na()
preschool_more_susp
```
Students who received one or more in-school suspension, by race/etchnicity, gender, disability status
```{r}
one_in_susp <- susp %>% 
  select (1:8, 51:68, 105: 124 )
one_in_susp[one_in_susp < 0] <- NA

one_in_susp<- one_in_susp %>% 
  drop_na()
one_in_susp
```

Students who received one out-of-school suspension, by race/etchnicity, gender, disability status

```{r}
one_out_susp <- susp %>% 
  select (1:8, 69:86, 125: 144 )
one_out_susp[one_out_susp < 0] <- NA

one_out_susp<- one_out_susp %>% 
  drop_na()
one_out_susp
```

Students who received more than one out-of-school suspension, by race/etchnicity, gender, disability status
```{r}

more_out_susp <- susp %>% 
  select (1:8, 87:104, 145: 167 )
more_out_susp[more_out_susp < 0] <- NA

more_out_susp<- more_out_susp%>% 
  drop_na()
more_out_susp
```
School days missed by gender, race, and disability status

```{r}
days_missed <- susp %>% 
  select (1:8, 168:189 )
days_missed[days_missed < 0] <- NA

days_missed <- days_missed %>% 
  drop_na()
days_missed
```

